A Formal Model of Checked C

### 2023-01-15 sandp23/implementation.tex
Minor
Adding Implementation

For instance, consider that in~\cregion, we want to string concat~\code{n} characters from tainted pointer~\code{t_str} to~\code{dst} (a checked pointer).
We cannot use~\code{strncat} because our type-checker restricts this as it expects both the pointers to be non-tainted as we are in~\cregion.
We need to either implement the logic for string concatenation in~\cregion or first copy the contents of~\code{t_str} into a~\cregion temporary buffer (sat~\code{tmp}) and then invoke~\code{strncat(dst, tmp, n);}.
Both of these approaches are inefficient and, if not done correctly, might result in security bugs.
If the developer knows that~\code{strncat} accesses only~\code{n} bytes from the source buffer, she would like to directly use~\code{strncat} with tainted source pointer in~\cregion.
The~\code{_TLIB} qualifier enables this as shown below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
// Put your example annotation here.
// First, manually check the memory is in tainted region.
// if yes, then call strncpy.
if (!is_mem_in_range(t_str, t_str + n, SBX_LOW(), SBX_HIGH()))
  handle_violation();
// our type checker ignores this because 
// the above _TLIB annotation.
strncat(dst, t_str, n);
\end{minted}
\aravind{Arun, Fix the above code. i.e., Add \_TLIB annotation to strncpy }
The above qualifier relaxes type-checking for all the arguments to the calls to~\code{strncat}, enabling the developer to use the function freely in~\cregion.

@@

\noindent\emph{Handling Tainted Buffers in~\cregion}:
All buffers that are marked as tainted in~\cregion should be allocated in the sandbox. For instance,~\code{buff} in function~\code{handle_request} of~\lst{lst:final}.
We perform source rewriting and make the buffer into a pointer variable and allocate the corresponding number of bytes using the sandbox-specific allocator. For instance, we perform the following rewriting for~\code{buff} in~\lst{lst:final} with WASM sandbox.
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{diff}
- char buff[MAX_MSG_SIZE] __Tainted;
+ char *buff = ....
\end{minted}
\aravind{Arun, please fix the above example on how exactly we replace it with WASM allocator.}
Note that we also add the necessary deallocator calls at function exit points.

@@

@@

The general guidelines for this alternative use case are shown in~\fig{fig:mixedmodesupport}.
It is best to annotate all functions with checked types for security purposes. However, if it is difficult to convert all functions, it may be more practical to only mark certain high-risk functions with a high probability of vulnerabilities as tainted. This allows for a flexible partitioning system that balances the need for security assurance with the overhead of converting to~\checkedc.
\aravind{Change title of this section and say that this mode has no guarentees and move this before evaluation.}

\iffalse

>>>>

For instance, consider that in~\cregion, we want to string concat~\code{n} characters from tainted pointer~\code{t_str} to~\code{dst} (a checked pointer).
We cannot use~\code{strncat} because our type-checker restricts this as it expects both the pointers to be non-tainted as we are in~\cregion.
We need to either implement the logic for string concatenation in~\cregion or first copy the contents of~\code{t_str} into a~\cregion temporary buffer (sat~\code{tmp}) and then invoke~\code{strncat(dst, tmp, n);}.
Both of these approaches are inefficient and, if not done correctly, might result in security bugs.
If the developer knows that~\code{strncat} accesses only~\code{n} bytes from the source buffer, she would like to directly use~\code{strncat} with tainted source pointer in~\cregion.
The~\code{_TLIB} qualifier enables this as shown below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
// Put your example annotation here.
// First, manually check the memory is in tainted region.
// if yes, then call strncpy.
if (!is_mem_in_range(t_str, t_str + n, SBX_LOW(), SBX_HIGH()))
  handle_violation();
// our type checker ignores this because 
// the above _TLIB annotation.
strncat(dst, t_str, n);
\end{minted}
\aravind{Arun, Fix the above code. i.e., Add \_TLIB annotation to strncpy }
The above qualifier relaxes type-checking for all the arguments to the calls to~\code{strncat}, enabling the developer to use the function freely in~\cregion.
Note that developer needs to manually add the check before calling~\code{strcat}.

@@

\iffalse
\noindent\emph{Handling Tainted Buffers in~\cregion}:
All buffers that are marked as tainted in~\cregion should be allocated in the sandbox. For instance,~\code{buff} in function~\code{handle_request} of~\lst{lst:final}.
We perform source rewriting and make the buffer into a pointer variable and allocate the corresponding number of bytes using the sandbox-specific allocator. For instance, we perform the following rewriting for~\code{buff} in~\lst{lst:final} with WASM sandbox.
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{diff}
- char buff[MAX_MSG_SIZE] __Tainted;
+ char *buff = ....
\end{minted}
\aravind{Arun, please fix the above example on how exactly we replace it with WASM allocator.}
Note that we also add the necessary deallocator calls at function exit points.
\fi

@@

Our type checker verifies the constraints (\fig{fig:type-system-1}) and displays violations as errors, enabling developers to make additional annotations.
For instance, for the code in~\lst{lst:final}, our type checker emits an error saying that ``~\emph{buffer~\code{buff} is tainted, but it is allocated in~\cregion}''.
Consequently, the developer has to make the following changes to allocate~\code{buff} in the sandbox:
\begin{minted}[mathescape, escapeinside=||, fontsize=\tiny]{diff}
- char buff[MAX_MSG_SIZE] _Tainted;
+ _t_Array_ptr<char> buff: count(MAX_MSG_SIZE)
+    = sbx_allocate(MAX_MSG_SIZE);
...
+ sbx_free(buff)
return rc;
\end{minted}

@@

The general guidelines for this alternative use case are shown in~\fig{fig:mixedmodesupport}.
It is best to annotate all functions with checked types for security purposes. However, if it is difficult to convert all functions, it may be more practical to only mark certain high-risk functions with a high probability of vulnerabilities as tainted. This allows for a flexible partitioning system that balances the need for security assurance with the overhead of converting to~\checkedc.
We add the additional constraint of not allowing casting from taint types to generic types to enable this generic use case without violating the safety guarantees of~\systemname.
Specifically, we disallow the following casting in~\cregion:
\begin{minted}[mathescape, escapeinside=||, fontsize=\tiny]{diff}
//_t_Ptr<int> y; int *z;
|\faRemove| z = (int *)y; // Not allowed.
\end{minted}
\iffalse
